Stable Neo-Hookean Flesh Simulation

### 2019-07-16 LaTeX-Master-Vorlage/chapter/paper.tex
First Commit, upload already existing files

\chapter{Background} \label{c:Background}
This chapter will provide the necessary background in continuum mechanics and mathematics in order to understand the next chapters.

In this chapter we will examine the topic of the paper \textit{Stable Neo-Hookean Flesh Simulation}. The goal of the paper was to model deformations for virtual characters that have human-like features.

\section{Notation}
At first we will declare the notation used in this thesis to avoid misunderstandings. We will use the common notation used in continuum mechanics.

\section{Mathematical Background}

Since mathematics plays an important role in our field of interest we will build a solid background in this chapter. A basic understanding of linear algebra is assumed.

\subsection{Matrices}
At first we will discuss the geometrical meaning of some common matrix properties.

\subsection{Singular Value Decomposition}

The singular value decomposition (SVD) will play an important role in the following. It is important for our application since it represents the best possible approximation of a given matrix by a matrix of low rank. This approximation can be looked at as a compression of the data given (\cite{LiesenMehrmann2015}, S. 295).

\section{Continuum Mechanics}
In this section we will give a broad introduction the field of Continuum Mechanics.
In Continuum Mechanics we are less interested in small particles like atoms or molecules of an object but concentrate on pieces of matter which are in comparison very large. We are therefore concerned with the mechanical behavior of solids and fluids on the macroscopic scale (\cite{Spencer1980}, S. 1).

@@

\[
F = \left[ \,f_0\, \bigg| \,f_1\, \bigg| \,f_2\, \right] = \begin{bmatrix} f_0 & f_3 & f_6 \\ f_1 & f_4 & f_7 \\ f_2 & f_5 & f_8 \end{bmatrix}
\]

>>>>

\chapter{Paper} \label{c:Paper}
In this chapter we will examine the topic of the paper \textit{Stable Neo-Hookean Flesh Simulation}. The goal of the paper was to model deformations for virtual characters that have human-like features.

@@

\[ F =  \begin{bmatrix}
  		f_0 & f_3 & f_6 \\
  		f_1 & f_4 & f_7 \\
  		f_2 & f_5 & f_8 \\
		\end{bmatrix} 
\]
